|

### 2025-02-19 paper.Rmd
Add files via upload
Change in the mathematical details of the full model (making more precise that the correlation b/w genotypes for the BYM2 priors apply to the spatially-structured effects), page 42 of Supplementary Files.

```{r}
eurosurveillance <- 0
if(eurosurveillance == 1){
text_sup <- "This supplementary material is hosted by Eurosurveillance as supporting information alongside the article 'High-risk human papillomavirus cervical infection prevalence in France, 2020-2023: a nationwide, large-scale, and spatially resolved retrospective study comparing opportunistic and organised screening', on behalf of the authors, who remain responsible for the accuracy and appropriateness of the content. The same standards for ethics, copyright, attributions and permissions as for the article apply. Supplements are not edited by Eurosurveillance and the journal is not responsible for the maintenance of any links or email addresses provided therein."
}else{
text_sup <- "Supplementary Files for the article 'High-risk human papillomavirus cervical infection prevalence in France, 2020-2023: a nationwide, large-scale, and spatially resolved retrospective study comparing opportunistic and organised screening."}

@@

HPC logs are available on the Github webpage: \url{https://github.com/osupplisson/hpv_prevalence/tree/main/log_hpc}.

@@

\begin{equation*}
\begin{cases}\text{Observation level}
\begin{cases}
y_{s} \sim \mathcal{B}\left(N_{s},p_{s}\right)\\
\begin{cases}
p_{s}=\frac{1}{1+\exp\left(-\mu_{s}\right)}\\
\\
\mu_{s}=\psi_0 + \mathbb{1}_{g_s=2} \psi_1 + v_{\text{SPACE}}(z_s,g_{s})+\gamma_{\text{AGE}}(a_{s},g_{s}) +\beta_{\text{TIME}}(t_s,g_{s})+\\
\mathbb{1}_{c_s = 2}\left[\psi_2 + \mathbb{1}_{g_s=2} \psi_3 + v'_{\text{SPACE}}(z_s,g_{s})+\gamma'_{\text{AGE}}(a_{s},g_{s}) +\beta'_{\text{TIME}}(t_s,g_{s})\right]~\text{Model 1 and 2}\\
\\
\mu_{s}=\psi_0 + \mathbb{1}_{g_s=2} \psi_1 + \alpha_{\text{SPACE}}(z_s,g_{s})+\gamma_{\text{AGE}}(a_{s},g_{s}) +\beta_{\text{TIME}}(t_s,g_{s})+\\
\mathbb{1}_{c_s = 2}\left[\psi_2 + \mathbb{1}_{g_s=2} \psi_3 + \alpha'_{\text{SPACE}}(z_s,g_{s})+\gamma'_{\text{AGE}}(a_{s},g_{s}) +\beta'_{\text{TIME}}(t_s,g_{s})\right]~\text{Model 3 to 6}\\
\end{cases}
\end{cases}\\
\text{Parameters}
\begin{cases}
\psi_{0}\sim \mathcal{N}\left(0,10\right)\\
\psi_{j\in\lbrace 1,2,3\rbrace}\sim \mathcal{N}\left(0,\sigma_{\psi_{j\in\lbrace 1,2,3\rbrace}}^2\right)\\
\text{Hyperparameters for } \psi_{j\in\lbrace 1,2,3\rbrace}
\begin{cases}
\sigma_{\psi_{j\in\lbrace 1,2,3\rbrace}} \sim \mathcal{PC}_{\sigma}\left(1,0.5\right)\\
\end{cases}\\
\textbf{RW2 for age and exchangeable correlation structure between genotypes}\\
\mathrm{for}~f\in\{\gamma,\gamma'\},~(g_s,g_s')\in\{1,2\}^2,~(a_s,a_s')\in \lbrace 1,\cdots,36\rbrace^2:\\
\mathrm{Latent~field}
\begin{cases}
f_{\text{AGE}}(a_s,g_s)-2f_{\text{AGE}}(a_s+1,g_s) + f_{\text{AGE}}(a_s+2,g_s)\sim\mathcal{N}\left(0,\sigma^2\right)\\
\mathrm{Corr}(f_{\text{AGE}}(a_s, 1),f_{\text{AGE}}(a_s', 2)) =\eta_{f_{\text{AGE}}}
\end{cases}\\
\mathrm{Hyperparameters}
\begin{cases}
\eta_{f_{\text{AGE}}}=  \frac{\exp(\eta_{f_{\text{AGE}}}^*) - 1}{\exp(\eta_{f_{\text{AGE}}}^*) + 2 - 1}\\
\eta_{f_{\text{AGE}}}^* \sim \mathcal{N}\left(0,5\right)\\\sigma_{f_{\text{AGE}}} \sim \mathcal{PC}_{\sigma}\left(\lambda_{\sigma_{f_{\text{AGE}}}}\right)\\
\lambda_{\sigma_{f_\text{AGE}}} = -\frac{-\log\left(p_{\sigma_{f_\text{AGE}}}\right)}{\sigma_{0}},~\Pr\left(\sigma >\sigma_{0}\right)=p_{\sigma_{f_\text{AGE}}}\\
\left(\sigma_{0},p_{\sigma_{f_\text{AGE}}}\right)=\left(10,0.01\right) \\
\end{cases}\\
\textbf{RW2 for time and exchangeable correlation structure between genotypes}\\
\mathrm{for}~f\in\{\beta,\beta'\},~(g_s,g_s')\in\{1,2\}^2,~(t_s,t_s')\in \lbrace 1,\cdots,174\rbrace^2:\\
\mathrm{Latent~field}
\begin{cases}
f_{\text{TIME}}(t_s,g_s)-2f_{\text{TIME}}(t_s+1,g_s) + f_{\text{TIME}}(t_s+2,g_s)\sim \mathcal{N}\left(0,\sigma^2\right)\\
\mathrm{Corr}(f_{\text{TIME}}(t_s, 1),f_{\text{TIME}}(t_s', 2)) =\eta_{f_{\text{TIME}}}
\end{cases}\\
\mathrm{Hyperparameters}
\begin{cases}
\eta_{f_{\text{TIME}}}=  \frac{\exp(\eta_{f_{\text{TIME}}}^*) - 1}{\exp(\eta_{f_{\text{TIME}}}^*) + 2 - 1}\\
\eta_{f_{\text{TIME}}}^* \sim \mathcal{N}\left(0,5\right)\\\sigma_{f_{\text{TIME}}} \sim \mathcal{PC}_{\sigma}\left(\lambda_{\sigma_{f_{\text{TIME}}}}\right)\\
\lambda_{\sigma_{f_\text{TIME}}} = -\frac{-\log\left(p_{\sigma_{f_\text{TIME}}}\right)}{\sigma_{0}},~\Pr\left(\sigma >\sigma_{0}\right)=p_{\sigma_{f_\text{TIME}}}\\
\left(\sigma_{0},p_{\sigma_{f_\text{TIME}}}\right)=\left(10,0.01\right) \\
\end{cases}\\
...\text{see next page}
\end{cases}\\
\end{cases}\\
\end{equation*}
\newpage

@@

\begin{equation*}
\begin{cases}
\mathrm{Parameters}
\begin{cases}
...next\\
\textbf{Models 3 to 6, spatial GMRF: GMRF with BYM2 structure for space}\\
\textbf{and exchangeable correlation structure between genotypes}\\
\mathrm{for}~f\in\{\alpha,\alpha'\},~(g_s,g_s')\in\{1,2\}^2,~\forall(z_s,z_s')\in \text{Set of postcodes}^2:\\
\mathrm{Latent~field}
\begin{cases}
f_{SPACE}(z_s,g_s) \sim 
BYM2\left(\sigma,\phi,R\right)\\
\mathrm{Corr}(f_{\text{SPACE}}(z_s, 1),f_{\text{SPACE}}(z_s, 2)) =\eta_{f_{\text{SPACE}}}
\end{cases}\\
\mathrm{Hyperparameters}
\begin{cases}
\eta_{f_{\text{SPACE}}}=  \frac{\exp(\eta_{f_{\text{SPACE}}}^*) - 1}{\exp(\eta_{f_{\text{SPACE}}}^*) + 2 - 1}\\
\eta_{f_{\text{SPACE}}}^* \sim \mathcal{N}\left(0,5\right)\\
\phi_{f_{SPACE}} \sim \mathcal{PC}_{\phi}\left(\lambda_{f_{SPACE}}\right)\\
\lambda_{f_{SPACE}} = \arg_{\in \mathbb{R}^+}: \Pr_{\lambda_{\sigma_{f_{\phi_{\text{SPACE}}}}}}\left(\phi_{f_{\text{SPACE}}}\leq\phi_{0}\right)=p_{\phi_{f_{\text{SPACE}}}}\\
\sigma_{f_{SPACE}} \sim \mathcal{PC}_{\sigma}\left(\lambda_{\sigma_{f_{SPACE}}}\right)\\
\lambda_{\sigma_{f_{SPACE}}} = -\frac{-\log\left(p_{\sigma_{f_{SPACE}}}\right)}{\sigma_{0}},~\Pr\left(\sigma >\sigma_{0}\right)=p_{\sigma_{f_{SPACE}}}\\
\left(\sigma_{0},p_{\sigma_{f_{SPACE}}}\right)=\left(10,0.01\right) \\
\left(\phi_{0},p_{\phi_{f_{SPACE}}}\right)=\left(0.5,0.5\right) \\
R: \begin{cases} 
\text{Delaunay Triangulation (model 3)}\\
\text{SOI subgraph of the Delaunay Triangulation (model 4)} \\
\text{1st-order Queen contiguity (model 5)} \\ 
\text{2nd-order Queen contiguity (model 6)} \\ 
\end{cases}
\end{cases}
\end{cases}
\end{cases}
\end{equation*}
\newpage

>>>>

```{r}
eurosurveillance <- 1
if(eurosurveillance == 1){
text_sup <- "This supplementary material is hosted by Eurosurveillance as supporting information alongside the article 'High-risk human papillomavirus cervical infection prevalence in France, 2020-2023: a nationwide, large-scale, and spatially resolved retrospective study comparing opportunistic and organised screening', on behalf of the authors, who remain responsible for the accuracy and appropriateness of the content. The same standards for ethics, copyright, attributions and permissions as for the article apply. Supplements are not edited by Eurosurveillance and the journal is not responsible for the maintenance of any links or email addresses provided therein."
}else{
text_sup <- "Supplementary Files for the article 'High-risk human papillomavirus cervical infection prevalence in France, 2020-2023: a nationwide, large-scale, and spatially resolved retrospective study comparing opportunistic and organised screening."}

@@

@@

\begin{equation*}
\begin{cases}\text{Observation level}
\begin{cases}
y_{s} \sim \mathcal{B}\left(N_{s},p_{s}\right)\\
\begin{cases}
p_{s}=\frac{1}{1+\exp\left(-\mu_{s}\right)}\\
\\
\mu_{s}=\psi_0 + \mathbb{1}_{g_s=2} \psi_1 + v_{\text{SPACE}}(z_s,g_{s})+\gamma_{\text{AGE}}(a_{s},g_{s}) +\beta_{\text{TIME}}(t_s,g_{s})+\\
\mathbb{1}_{c_s = 2}\left[\psi_2 + \mathbb{1}_{g_s=2} \psi_3 + v'_{\text{SPACE}}(z_s,g_{s})+\gamma'_{\text{AGE}}(a_{s},g_{s}) +\beta'_{\text{TIME}}(t_s,g_{s})\right]~\text{Model 1 and 2}\\
\\
\mu_{s}=\psi_0 + \mathbb{1}_{g_s=2} \psi_1 + \alpha_{\text{SPACE}}(z_s,g_{s})+\gamma_{\text{AGE}}(a_{s},g_{s}) +\beta_{\text{TIME}}(t_s,g_{s})+\\
\mathbb{1}_{c_s = 2}\left[\psi_2 + \mathbb{1}_{g_s=2} \psi_3 + \alpha'_{\text{SPACE}}(z_s,g_{s})+\gamma'_{\text{AGE}}(a_{s},g_{s}) +\beta'_{\text{TIME}}(t_s,g_{s})\right]~\text{Model 3 to 6}\\
\end{cases}
\end{cases}\\
\text{Parameters}
\begin{cases}
\psi_{0}\sim \mathcal{N}\left(0,10\right)\\
\psi_{j\in\lbrace 1,2,3\rbrace}\sim \mathcal{N}\left(0,\sigma_{\psi_{j\in\lbrace 1,2,3\rbrace}}^2\right)\\
\text{Hyperparameters for } \psi_{j\in\lbrace 1,2,3\rbrace}
\begin{cases}
\sigma_{\psi_{j\in\lbrace 1,2,3\rbrace}} \sim \mathcal{PC}_{\sigma}\left(1,0.5\right)\\
\end{cases}\\
\textbf{RW2 for age and exchangeable correlation structure between genotypes}\\
\mathrm{for}~f\in\{\gamma,\gamma'\},~(g_s,g_s')\in\{1,2\}^2,~(a_s,a_s')\in \lbrace 1,\cdots,36\rbrace^2:\\
\mathrm{Latent~field}
\begin{cases}
f_{\text{AGE}}(a_s,g_s)-2f_{\text{AGE}}(a_s+1,g_s) + f_{\text{AGE}}(a_s+2,g_s)\sim\mathcal{N}\left(0,\sigma^2\right)\\
\mathrm{Corr}(f_{\text{AGE}}(a_s, 1),f_{\text{AGE}}(a_s, 2)) =\eta_{f_{\text{AGE}}}
\end{cases}\\
\mathrm{Hyperparameters}
\begin{cases}
\eta_{f_{\text{AGE}}}=  \frac{\exp(\eta_{f_{\text{AGE}}}^*) - 1}{\exp(\eta_{f_{\text{AGE}}}^*) + 2 - 1}\\
\eta_{f_{\text{AGE}}}^* \sim \mathcal{N}\left(0,5\right)\\\sigma_{f_{\text{AGE}}} \sim \mathcal{PC}_{\sigma}\left(\lambda_{\sigma_{f_{\text{AGE}}}}\right)\\
\lambda_{\sigma_{f_\text{AGE}}} = -\frac{-\log\left(p_{\sigma_{f_\text{AGE}}}\right)}{\sigma_{0}},~\Pr\left(\sigma >\sigma_{0}\right)=p_{\sigma_{f_\text{AGE}}}\\
\left(\sigma_{0},p_{\sigma_{f_\text{AGE}}}\right)=\left(10,0.01\right) \\
\end{cases}\\
\textbf{RW2 for time and exchangeable correlation structure between genotypes}\\
\mathrm{for}~f\in\{\beta,\beta'\},~(g_s,g_s')\in\{1,2\}^2,~(t_s,t_s')\in \lbrace 1,\cdots,174\rbrace^2:\\
\mathrm{Latent~field}
\begin{cases}
f_{\text{TIME}}(t_s,g_s)-2f_{\text{TIME}}(t_s+1,g_s) + f_{\text{TIME}}(t_s+2,g_s)\sim \mathcal{N}\left(0,\sigma^2\right)\\
\mathrm{Corr}(f_{\text{TIME}}(t_s, 1),f_{\text{TIME}}(t_s, 2)) =\eta_{f_{\text{TIME}}}
\end{cases}\\
\mathrm{Hyperparameters}
\begin{cases}
\eta_{f_{\text{TIME}}}=  \frac{\exp(\eta_{f_{\text{TIME}}}^*) - 1}{\exp(\eta_{f_{\text{TIME}}}^*) + 2 - 1}\\
\eta_{f_{\text{TIME}}}^* \sim \mathcal{N}\left(0,5\right)\\\sigma_{f_{\text{TIME}}} \sim \mathcal{PC}_{\sigma}\left(\lambda_{\sigma_{f_{\text{TIME}}}}\right)\\
\lambda_{\sigma_{f_\text{TIME}}} = -\frac{-\log\left(p_{\sigma_{f_\text{TIME}}}\right)}{\sigma_{0}},~\Pr\left(\sigma >\sigma_{0}\right)=p_{\sigma_{f_\text{TIME}}}\\
\left(\sigma_{0},p_{\sigma_{f_\text{TIME}}}\right)=\left(10,0.01\right) \\
\end{cases}\\
...\text{see next page}
\end{cases}\\
\end{cases}\\
\end{equation*}
\newpage

@@

\begin{equation*}
\begin{cases}
\mathrm{Parameters}
\begin{cases}
...next\\
\textbf{Models 3 to 6, spatial GMRF: GMRF with BYM2 structure for space}\\
\textbf{and exchangeable correlation structure between genotypes}\\
\mathrm{for}~f\in\{\alpha,\alpha'\},~(g_s,g_s')\in\{1,2\}^2,~\forall(z_s,z_s')\in \text{Set of postcodes}^2:\\
\mathrm{Latent~field}
\begin{cases}
f_{SPACE}(z_s,g_s) \sim 
BYM2\left(\sigma,\phi,R\right) \\
\Leftrightarrow \begin{cases}
f_{SPACE}(z_s,g_s) = \frac{1}{\sqrt{\tau_{f_{\text{SPACE}}}}}\left(\sqrt{1-\phi_{f_{\text{SPACE}}}}v(z_s,g_s)+\phi_{f_{\text{SPACE}}} u(z_s,g_s)\right)\\
v(z_s,g_s) \sim \mathcal{N}\left(0,1\right) \\
u(g_s) \sim \mathcal{N}\left(0,R_*^{-}\right) \\
\end{cases}\\
\mathrm{Corr}(u(z_s, 1),u(z_s, 2)) =\eta_{f_{\text{SPACE}}}
\end{cases}\\
\mathrm{Hyperparameters}
\begin{cases}
\eta_{f_{\text{SPACE}}}=  \frac{\exp(\eta_{f_{\text{SPACE}}}^*) - 1}{\exp(\eta_{f_{\text{SPACE}}}^*) + 2 - 1}\\
\eta_{f_{\text{SPACE}}}^* \sim \mathcal{N}\left(0,5\right)\\
\phi_{f_{SPACE}} \sim \mathcal{PC}_{\phi}\left(\lambda_{f_{SPACE}}\right)\\
\lambda_{f_{SPACE}} = \arg_{\in \mathbb{R}^+}: \Pr_{\lambda_{\sigma_{f_{\phi_{\text{SPACE}}}}}}\left(\phi_{f_{\text{SPACE}}}\leq\phi_{0}\right)=p_{\phi_{f_{\text{SPACE}}}}\\
\sigma_{f_{SPACE}} \sim \mathcal{PC}_{\sigma}\left(\lambda_{\sigma_{f_{SPACE}}}\right)\\
\lambda_{\sigma_{f_{SPACE}}} = -\frac{-\log\left(p_{\sigma_{f_{SPACE}}}\right)}{\sigma_{0}},~\Pr\left(\sigma >\sigma_{0}\right)=p_{\sigma_{f_{SPACE}}}\\
\left(\sigma_{0},p_{\sigma_{f_{SPACE}}}\right)=\left(10,0.01\right) \\
\left(\phi_{0},p_{\phi_{f_{SPACE}}}\right)=\left(0.5,0.5\right) \\
R :\begin{cases} 
\text{Delaunay Triangulation (model 3)}\\
\text{SOI subgraph of the Delaunay Triangulation (model 4)} \\
\text{1st-order Queen contiguity (model 5)} \\ 
\text{2nd-order Queen contiguity (model 6)} \\ 
\end{cases}\\
R_*:~\text{scaled counterpart of the matrix R}
\end{cases}
\end{cases}
\end{cases}
\end{equation*}
\newpage
